---
title: "Assignment"
author: "LiYueting"
date: "7/16/2021"
output: html_document
---

```{r setup, include=FALSE}
options(himltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina=3, ###give higher resolution than 1
                      echo = TRUE, ###desplay code chunk
                      eval = TRUE, ###execute the code chunk
                      message = TRUE, ###give error message
                      warning = TRUE) ###give error messages
```

### import packages
```{r}
packages = c('igraph','tidygraph',
             'ggraph','visNetwork',
             'lubridate','clock',
             'tidyverse',"tm",
             'tidytext', 
             'widyr', 'wordcloud',
             'DT', 'ggwordcloud', 
             'textplot','hms',
             'tidygraph', 'ggraph',
             'igraph')
for(p in packages){
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```
### read in data source
```{r}
GAStech_nodes <- read_csv("data source/MC1/EmployeeRecords.csv")
GAStech_edges <- read_csv("data source/MC1/email headers.csv")
```

```{r}
glimpse(GAStech_nodes)
```

```{r}
GAStech_nodes$Name <- paste(GAStech_nodes$FirstName,GAStech_nodes$LastName)
GAStech_nodes$Name <- gsub(" ",".",GAStech_nodes$Name)
GAStech_nodes$id <- c(1:nrow(GAStech_nodes))
GAStech_nodes$military[GAStech_nodes$MilitaryDischargeDate != "NA"] <- "YES"
GAStech_nodes$military[is.na(GAStech_nodes$military)] <- "NO"
```

### change data type
```{r}
GAStech_nodes$BirthDate = mdy(GAStech_nodes$BirthDate)
GAStech_nodes$CitizenshipStartDate = mdy(GAStech_nodes$CitizenshipStartDate)
GAStech_nodes$PassportIssueDate = mdy(GAStech_nodes$PassportIssueDate)
GAStech_nodes$PassportExpirationDate = mdy(GAStech_nodes$PassportExpirationDate)
GAStech_nodes$CurrentEmploymentStartDate = mdy(GAStech_nodes$CurrentEmploymentStartDate)
GAStech_nodes$MilitaryDischargeDate = mdy(GAStech_nodes$MilitaryDischargeDate)
```

### Switch column orders
```{r}
GAStech_nodes <- GAStech_nodes[, c(20, 19, 15, 12, 13, 4:8, 21, 1:3, 9:11, 14, 16:18)]
GAStech_nodes$Name <- tolower(GAStech_nodes$Name)
```

```{r}
GAStech_nodes_new <- GAStech_nodes
GAStech_nodes_new$Name[GAStech_nodes_new$Name == "sten.sanjorge.jr."] <- "sten.sanjorge.jr"
```

```{r}
glimpse(GAStech_nodes_new)
```


### process edges
```{r}
glimpse(GAStech_edges)
```

###to process gestech edges data
```{r}
GAStech_edges_new <- GAStech_edges %>% 
  separate_rows(To)
```

### data cleaning

```{r}
GAStech_edges_new$From <- removeWords(GAStech_edges_new$From, "@gastech.com.kronos")
```


### Change format
```{r}
GAStech_edges_new$Date <- mdy_hm(GAStech_edges_new$Date)
GAStech_edges_new$Weekday <-  wday(GAStech_edges_new$Date,
                                 label = TRUE,
                                 abbr = FALSE)
```


```{r}
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$From != "gastech.com.kronos",]
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$To != "gastech.com.kronos",]
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$From != "@gastech.com.tethys",]
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$To != "@gastech.com.tethys",]
```

```{r}
GAStech_edges_new$From <- tolower(GAStech_edges_new$From)
GAStech_edges_new$To <- tolower(GAStech_edges_new$To)
```

```{r}
GAStech_edges_new$From[GAStech_edges_new$From == "sten.sanjorge jr."] <- "sten.sanjorge.jr"
```

### remove emails that sent to themselves
```{r}
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$To != GAStech_edges_new$From,]
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$Weekday != "NA",]
```

```{r}
glimpse(GAStech_edges_new)
```

### keep data only from given edges
```{r}
vc <- unique(GAStech_nodes_new$Name)
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$From %in% vc,]
GAStech_edges_new <- GAStech_edges_new[GAStech_edges_new$To %in% vc,]
```

```{r}
glimpse(GAStech_edges_new)
```
### label from to use the infor from nodes

```{r}
nodes_ref <- GAStech_nodes_new[,1:2]
colnames(nodes_ref) <- c("Source", "From")
GAStech_edges_new1 <- merge(GAStech_edges_new, nodes_ref[, c("Source", "From")], by="From")
colnames(nodes_ref) <- c("Target", "To")
GAStech_edges_new1 <- merge(GAStech_edges_new1, nodes_ref[, c("Target", "To")], by="To")
```

```{r}
glimpse(GAStech_edges_new1)
```

```{r}
GAStech_edges_aggregated <- GAStech_edges_new1 %>%
  group_by(Source, Target, Weekday) %>%
    summarise(Weight = n()) %>%
  filter(Weight > 1) %>%
  ungroup()
```


```{r}
glimpse(GAStech_edges_aggregated)
```

```{r}
GAStech_graph <- tbl_graph(nodes = GAStech_nodes_new,
                           edges = GAStech_edges_aggregated, 
                           directed = TRUE)
```

```{r}
GAStech_graph
```

```{r}
GAStech_graph %>%
  activate(edges) %>%
  arrange(desc(Weight))
```

###Plotting network graph
```{r}
g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes(colour = 'grey50')) +
  geom_node_point(aes(colour = 'grey40'))
g + theme_graph(background = 'grey10',
                text_colour = 'white')
```

###Fruchterman and Reingold layout
```{r}
g <- ggraph(GAStech_graph, 
            layout = "fr") +
  geom_edge_link(aes()) +
  geom_node_point(aes())
g + theme_graph()
```

### whether have military background
```{r}
g <- ggraph(GAStech_graph, 
            layout = "nicely") +
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = military), 
                  size = 3)
g + theme_graph()
```

```{r}
set_graph_style() 
g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = CurrentEmploymentType), 
                  size = 2)
g + facet_edges(~Weekday) +
  th_foreground(foreground = "grey80",  
                border = TRUE) +
  theme(legend.position = 'bottom')
```

```{r}
set_graph_style()
g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = CurrentEmploymentType), 
                  size = 2)
g + facet_nodes(~CurrentEmploymentType)+
  th_foreground(foreground = "grey80",  
                border = TRUE) +
  theme(legend.position = 'bottom')
```

### betweenness
```{r}
g <- GAStech_graph %>%
  mutate(betweenness_centrality = centrality_betweenness()) %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = CurrentEmploymentType,
            size=betweenness_centrality))
g + theme_graph()+
    theme(legend.position = 'bottom')
```
### network
```{r}
g <- GAStech_graph %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = CurrentEmploymentType, 
                      size = centrality_betweenness()))
g + theme_graph()
```
### community
```{r}
g <- GAStech_graph %>%
  mutate(community = as.factor(group_edge_betweenness(weights = Weight, directed = TRUE))) %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = community))  
g + theme_graph()
```

```{r}
GAStech_edges_aggregated <- GAStech_edges_new1 %>%
  left_join(GAStech_nodes_new, by = c("From" = "Name")) %>%
  rename(from = id) %>%
  left_join(GAStech_nodes_new, by = c("To" = "Name")) %>%
  rename(to = id) %>%
  group_by(from, to) %>%
    summarise(weight = n()) %>%
  filter(from!=to) %>%
  filter(weight > 1) %>%
  ungroup()
```

```{r}
glimpse(GAStech_edges_aggregated)
```

## interactive
```{r}
visNetwork(GAStech_nodes_new, 
           GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr")
```


```{r}
GAStech_nodes_new <- GAStech_nodes_new %>%
  rename(group = CurrentEmploymentType)
```

### Nodes
```{r}
visNetwork(GAStech_nodes_new,
           GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visLegend() %>%
  visLayout(randomSeed = 123)
```

### edges
```{r}
visNetwork(GAStech_nodes_new,
           GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to", 
           smooth = list(enabled = TRUE, 
                         type = "curvedCW")) %>%
  visLegend() %>%
  visLayout(randomSeed = 123)

```
### add selection
```{r}
visNetwork(GAStech_nodes,
           GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visOptions(highlightNearest = TRUE,
             nodesIdSelection = TRUE) %>%
  visLegend() %>%
  visLayout(randomSeed = 123)
```

#### text analysis
```{r}
all_news <- "data source/MC1/News Articles/"
```

### infolder function
```{r}
read_folder <- function(infolder) {
  tibble(file = dir(infolder, 
                    full.names = TRUE)) %>%
    mutate(text = map(file, 
                      read_lines)) %>%
    transmute(id = basename(file), 
              text) %>%
    unnest(text)
}
```

### read in data
```{r}
raw_text <- tibble(folder = 
                     dir(all_news, 
                         full.names = TRUE)) %>%
  mutate(folder_out = map(folder, 
                          read_folder)) %>%
  unnest(cols = c(folder_out)) %>%
  transmute(newsgroup = basename(folder), 
            id, text)
write_rds(raw_text, "data source/MC1/rds/all_news.rds")
```

```{r}
raw_text_backup <- raw_text
```

```{r}
raw_text %>%
  group_by(newsgroup) %>%
  summarize(messages = n_distinct(id)) %>%
  ggplot(aes(messages,newsgroup)) +
  geom_col(fill = "lightblue") +
  labs(y = NULL)
```
### clean text
```{r}
raw_text1<-raw_text[!(raw_text$text==""|raw_text$text=="<< Continue reading the main story >>"),]
raw_text1<-raw_text1[!(raw_text1$text==" "|raw_text1$text=="<< to continue reading main history >>"),]
raw_text1<-raw_text1[!(raw_text1$text=="<< to continue reading main history >>"),]
```

```{r}
cleaned_text <- raw_text1 %>%
  filter(str_detect(text, "^[^>]+[A-Za-z\\d]")
         | text == "",
         !str_detect(text, 
                     "writes(:|\\.\\.\\.)$"),
         !str_detect(text, 
                     "^In article <"),
         !str_detect(text, 
                     "<<"),
         !str_detect(text,
                     "To continue reading main history"),
         !str_detect(text,
                     " to continue reading main history "),
         !str_detect(text,
                     "continue to read the principal history")
  )

```

### text analysis
```{r}
usenet_words <- cleaned_text %>%
  unnest_tokens(word, text) %>%
  filter(str_detect(word, "[a-z']$"),
         !word %in% stop_words$word)
```

```{r}
usenet_words %>%
  count(word, sort = TRUE)
```

```{r}
words_by_newsgroup <- usenet_words %>%
  count(newsgroup, word, sort = TRUE) %>%
  ungroup()
```

### word cloud demonstration
```{r}
wordcloud(words_by_newsgroup$word,
          words_by_newsgroup$n,
          max.words = 300)
```

### Visualising Words in newsgroups(take long to run)
```{r}
set.seed(1234)
words_by_newsgroup %>%
  filter(n > 0) %>%
ggplot(aes(label = word,
           size = n)) +
  geom_text_wordcloud() +
  theme_minimal() +
  facet_wrap(~newsgroup)
```

### Computing tf-idf within newsgroups
```{r}
tf_idf <- words_by_newsgroup %>%
  bind_tf_idf(word, newsgroup, n) %>%
  arrange(desc(tf_idf))
```

### Visualising tf-idf as interactive table
```{r}
DT::datatable(tf_idf, filter = 'top') %>% 
  formatRound(columns = c('tf', 'idf', 
                          'tf_idf'), 
              digits = 3) %>%
  formatStyle(0, 
              target = 'row', 
              lineHeight='25%')
```

### Visualising tf-idf within newsgroups
```{r}
tf_idf %>%
  group_by(newsgroup) %>%
  slice_max(tf_idf, 
            n = 5) %>%
  ungroup() %>%
  mutate(word = reorder(word, 
                        tf_idf)) %>%
  ggplot(aes(tf_idf, 
             word, 
             fill = newsgroup)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ newsgroup, 
             scales = "free") +
  labs(x = "tf-idf", 
       y = NULL)
```

### Counting and correlating pairs of words with the widyr package
```{r}
newsgroup_cors <- words_by_newsgroup %>%
  pairwise_cor(newsgroup, 
               word, 
               n, 
               sort = TRUE)
```

### Visualising correlation as a network
```{r}
set.seed(2017)
newsgroup_cors %>%
  filter(correlation > .7) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(alpha = correlation, 
                     width = correlation)) +
  geom_node_point(size = 6, 
                  color = "lightblue") +
  geom_node_text(aes(label = name),
                 color = "red",
                 repel = TRUE) +
  theme_void()
```

```{r}
set.seed(2017)
newsgroup_cors %>%
  filter(correlation > .75) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(alpha = correlation, 
                     width = correlation)) +
  geom_node_point(size = 6, 
                  color = "lightblue") +
  geom_node_text(aes(label = name),
                 color = "red",
                 repel = TRUE) +
  theme_void()
```


### Bigram
```{r}
bigrams <- cleaned_text %>%
  unnest_tokens(bigram, 
                text, 
                token = "ngrams", 
                n = 2)
```

```{r}
bigrams_count <- bigrams %>%
  filter(bigram != 'NA') %>%
  count(bigram, sort = TRUE)
```

```{r}
bigrams_separated <- bigrams %>%
  filter(bigram != 'NA') %>%
  separate(bigram, c("word1", "word2"), 
           sep = " ")
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)
```

```{r}
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
```

### Create a network graph from bigram data frame
```{r}
bigram_graph <- bigram_counts %>%
  filter(n > 40) %>%
  graph_from_data_frame()
bigram_graph
```

### Visualizing a network of bigrams with ggraph
```{r}
set.seed(123)
ggraph(bigram_graph, layout = "nicely") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), 
                 vjust = 0.7, 
                 hjust = 1)
```

```{r}
set.seed(1234)
a <- grid::arrow(type = "closed", 
                 length = unit(.15,
                               "inches"))
ggraph(bigram_graph, 
       layout = "nicely") +
  geom_edge_link(aes(edge_alpha = n), 
                 show.legend = FALSE,
                 arrow = a, 
                 end_cap = circle(.07,
                                  'inches')) +
  geom_node_point(color = "lightblue", 
                  size = 5) +
  geom_node_text(aes(label = name), 
                 vjust = 1, 
                 hjust = 1) +
  theme_void()
```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```



