---
title: "Assignment"
description: |
  The concepts, methods and techniques learned in class to solve real world problem using visual analytics techniques.
author:
  - name: Yueting Li
    url: https://linkedin.com/in/yueting-li-9ab569208
date: 07-25-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
options(himltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina=3, ###give higher resolution than 1
                      echo = TRUE, ###desplay code chunk
                      eval = TRUE, ###execute the code chunk
                      message = TRUE, ###give error message
                      warning = TRUE) ###give error messages
```

## 1. Assignment requirements
### Mini-Challenge 1
Mini-Challenge 1 looks at the relationships and conditions that led up to the kidnapping. As an analyst, you have a set of current and historical news reports at your disposal, as well as resumes of numerous GAStech employees and email headers from two weeks of internal GAStech company email. Can you identify the complex relationships among all of these people and organizations?

### Background
Note: This scenario and all the people, places, groups, technologies, contained therein are fictitious. Any resemblance to real people, places, groups, or technologies is purely coincidental.

In the roughly twenty years that Tethys-based GAStech has been operating a natural gas production site in the island country of Kronos, it has produced remarkable profits and developed strong relationships with the government of Kronos. However, GAStech has not been as successful in demonstrating environmental stewardship.

In January, 2014, the leaders of GAStech are celebrating their new-found fortune as a result of the initial public offering of their very successful company. In the midst of this celebration, several employees of GAStech go missing. An organization known as the Protectors of Kronos (POK) is suspected in the disappearances.

It is January 21, 2014, and as an expert in visual analytics, you have been tasked with helping people understand the complex relationships among people and organizations that may have contributed to these events.

### Tasks and Questions:
Mini-Challenge 1 looks at the relationships and conditions that led up to the kidnapping. As an analyst, you have a set of current and historical news reports at your disposal, as well as resumes of numerous GAStech employees and email headers from two weeks of internal GAStech company email. Can you identify the complex relationships among all of these people and organizations?

Use visual analytics to analyze the available data and develop responses to the questions below. In addition, prepare a video that shows how you used visual analytics to solve the challenge. 

1) Characterize the news data sources provided. Which are primary sources and which are derivative sources? What are the relationships between the primary and derivative sources? Please limit your answer to 8 images and 300 words.

2) Characterize any biases you identify in these news sources, with respect to their representation of specific people, places, and events. Give examples. Please limit your answer to 6 images and 500 words.

3) Given the data sources provided, use visual analytics to identify potential official and unofficial relationships among GASTech, POK, the APA, and Government. Include both personal relationships and shared goals and objectives. Provide evidence for these relationships. Please limit your answer to 6 images and 400 words.

4) If you solved this mini-challenge in 2014, how did you approach it differently this year?

## 2. Assignment answering
1) Characterize the news data sources provided. Which are primary sources and which are derivative sources? What are the relationships between the primary and derivative sources? Please limit your answer to 8 images and 300 words.

```{r}
packages = c('igraph','tidygraph',
             'ggraph','visNetwork',
             'lubridate','clock',
             'tidyverse',"tm",
             'tidytext', 
             'widyr', 'wordcloud',
             'DT', 'ggwordcloud', 
             'textplot','hms',
             'tidygraph', 'ggraph',
             'igraph')
for(p in packages){
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

```{r}
glimpse(GAStech_nodes)
```

This graph visualise the correlation between news data sources provided as a network
```{r}
set.seed(2017)
newsgroup_cors %>%
  filter(correlation > .7) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(alpha = correlation, 
                     width = correlation)) +
  geom_node_point(size = 6, 
                  color = "lightblue") +
  geom_node_text(aes(label = name),
                 color = "red",
                 repel = TRUE) +
  theme_void()

```